% Supplementary Material
\subsection{Overview of Datasets Included in BrainScape}

We provide a detailed table summarizing essential metadata for each dataset included in BrainScape. 
Table \ref{suppDataTable} provides information on the \NumDatasets\ MRI studies and datasets currently included in the BrainScape dataset.
As the project evolves, additional datasets will be added, further expanding this list. 
The following section describes the columns of the table.

\begin{enumerate}
    \item \textbf{Identifier}: Each dataset is assigned a unique identifier (e.g., ``AOMIC'', ``QTAB'') to facilitate referencing within BrainScape. 
    All MRI scans and associated metadata for each dataset are organized in dedicated folders named after their identifiers, ensuring traceability to the original source or study. 
    Hyperlinks embedded in the identifier column provide direct access to the corresponding source dataset repository.
    Some datasets may require authorization or the completion of specific user agreements for access.

    \item \textbf{Dataset Name}: This column lists the name of the dataset or study from which the anatomical MRI scans were obtained. 
    When applicable, a citation is included to acknowledge the contributions of the original dataset creators.

    \item \textbf{License}: This column specifies the licensing terms under which each dataset is made available. 
    Many datasets obtained through OpenNeuro (\cite{markiewicz2021openneuro}) are distributed under a CC0 license, allowing unrestricted reuse.
    However, some data sources (e.g., ABIDE (\cite{di2014autism}), ABIDE2 (\cite{di2017enhancing}), ADHD200 (\cite{adhd2012adhd}), CORR (\cite{zuo2014open}), CMIHBN (\cite{alexander2017open}), INDINKI (\cite{nooner2012nki})) are governed by CC-BY-NC or similarly restrictive licenses. 
    These datasets often require a signed user agreement, an approved access application, or both. 
    Users are responsible for reviewing and complying with all applicable licensing conditions before using these datasets. 
    
    \item \textbf{Subjects}:  This column reports the number of participants whose anatomical scans are included in this study.
    In some instances, this total may be lower than the number of participants in the original dataset because scans that failed visual quality inspections were excluded. 
    Records of these excluded subjects are maintained in the corresponding dataset metadata, allowing researchers to re-evaluate or reverse exclusion decisions if necessary.

    \item \textbf{T1w, T2w, and FLAIR}: These columns display the number of scans available for each MRI modality in every dataset. 
    Individual subjects may undergo multiple scanning sessions, which can result in scan counts exceeding the total number of subjects. 
\end{enumerate}

Note: gadolinium-enhanced T1-weighted (T1Gd) MRIs are only provided by the BRATS dataset, therefore this modality is not included in Table \ref{suppDataTable}.

% Inputting the Generated Suplimentary Table
\input{tables/supp_datasets_details_table.tex}

\subsection{Scanner Hardware and Magnetic Field Strengths}

Supplementary Table~\ref{tab:scanner_info} summarizes detailed information about the MRI scanner hardware 
used across the \NumDatasets\ datasets added to BrainScape dataset. 
The table provides comprehensive statistics for each imaging modality (T1w, T2w, FLAIR), organized by MRI scanner manufacturer, 
scanner model, and magnetic field strength (Tesla). 
The scanner details show the heterogeneity in the hardware diversity of the included datasets, 
facilitating downstream studies interested in evaluating generalization across different scanning hardware. 

\input{tables/supp_scanner_summary.tex}