\section*{Data and Code Availability}

All source code, default plugins, and dataset-specific configuration files required 
to reproduce the BrainScape workflow are openly available under the MIT licence at 
\url{https://github.com/yasinzaii/BrainScape}. Since BrainScape automatically integrates 
publicly available MRI data from multiple open repositories, no derivatives are distributed. 
Instead, any researcher can regenerate exactly the same derivatives locally by cloning the repository, 
and executing the workflow with the provided configuration files. 
This approach avoids the very large storage overhead of hosting duplicate derivatives, 
and preserves full provenance, since the choice of plugins and their parameters is recorded 
in every configuration file. 
For detailed usage instructions, please refer to the README file or contact the authors for further clarification.



\section*{Author Contributions}

\begin{enumerate}
    \item \textbf{Muhammad Nabi Yasinzai (MNY)}: Conceptualization, Methodology, Software, Writing - Original Draft.
    \item \textbf{Remika Mito (RM)}: Conceptualization, Supervision, Writing - Review \& Editing, Funding acquisition. 
    \item \textbf{Mangor Pedersen (MP)} Conceptualization, Supervision, Writing - Review \& Editing, Resources, Funding acquisition. 
\end{enumerate}
All authors read, revised, and approved the final version of the manuscript.


\section*{Funding}

MNY is a recipient of Australian Epilepsy Project PhD scholarship 
(Medical Research Future Fund - Frontier Health and Medical Research Program - 
Grant Numbers MRFF75908). 
RM is the recipient of an Australian Research Council Discovery Early Career 
Researcher Award (project number: DE240101035). 
MP is a recipient of Health Research Council fellowship, New Zealand (\#21/622).

\section*{Declaration of Competing Interests}

The authors declare that they have no competing financial or non-financial interests 
that could have influenced the work reported in this manuscript.

\section*{Acknowledgements}

We thank the participants in the original studies whose data make this work possible. 
Their contributions to open neuroimaging resources form the foundation of BrainScape's 
mission to build a broad, diverse, and evolving dataset.
