% Supplementary Material

To ensure transparency, we provide a detailed table summarizing essential metadata for each dataset included in this data integration framework. 
Table \ref{suppDataTable} presents a comprehensive inventory of all \NumDatasets\ MRI studies and datasets currently included in this framework.
As the project evolves, additional datasets will be incorporated, further expanding this list. This table provides in-depth 
information on each source dataset whose anatomical scans are included in the framework. The following sections provide a detailed description 
of the columns and their significance:

\begin{enumerate}
    \item \textbf{Identifier}: Each dataset is assigned a unique identifier (e.g., ``AOMIC'', ``QTAB'') to facilitate referencing within this framework and its source. 
    All MRI scans and associated metadata for each dataset are organized in dedicated folders named after their identifiers, ensuring traceability to the original source or study. 
    Hyperlinks embedded in the identifier column provide direct access to the corresponding repository, allowing immediate access to the source dataset.
    It is important to note that some datasets may require authorization or the completion of specific user agreements for access.

    \item \textbf{Dataset Name}: This column lists the name of the dataset or study from which the anatomical MRI scans were obtained. 
    When applicable, a citation is included to acknowledge the contributions of the original dataset creators.

    \item \textbf{License}: This column specifies the licensing terms under which each dataset is made available. 
    Many datasets obtained through OpenNeuro \cite{markiewicz2021openneuro} are distributed under a CC0 license, allowing unrestricted reuse.
    However, some data sources (e.g., ABIDE \cite{di2014autism}, ABIDE2, ADHD200 \cite{adhd2012adhd}, CORR \cite{zuo2014open}, CMIHBN, INDINKI \cite{nooner2012nki}) are governed by CC-BY-NC or licenses with similar restrictions.
    These licenses often require a signed user agreement, an approved access application, or both. Users are responsible for reviewing and complying with all applicable licensing conditions before utilizing the data. 
    
    \item \textbf{Subjects}:  This column reports the number of participants whose anatomical scans are included in this study.
    In some instances, the total may be lower than the number of participants in the original dataset, because scans failing visual quality inspections were excluded.
    Records of these excluded subjects are maintained in the corresponding dataset metadata, allowing researchers to re-evaluate or reverse exclusion decisions if necessary.

    \item \textbf{T1w, T2w, and FLAIR}: These columns display the quantity of each MRI modality available for each dataset. 
    It is important to note that individual subjects may undergo multiple scanning sessions, which can result in scan counts exceeding the total number of subjects. 
\end{enumerate}


% Inputting the Generated Suplimentary Table
\input{tables/supp_datasets_details_table.tex}